\sys: Automatic Disease Diagnosis Using Large Language Models and Answer Set Programming

### 2025-09-18 paper/draft.tex
Updates in intro

This work presents \sys, a framework for automatic disease prediction 
that encodes medical literature and transforms it into ASP code using an LLM. 
It describes the roles of both LLMs and ASP, emphasizing how each contributes to the overall framework. 
The \sys architecture is outlined, along with implementation details for constructing effective prompts 
and structuring rules within the ASP knowledge base.
The method includes predictions for a set of diseases based on the constructed knowledge bases. 
Results show that this approach achieves high-accuracy predictions and provides interpretable explanations.

Future work will focus on integrating retrieval-augmented generation (RAG) 
to ground ASP code in reliable medical sources, fine-tuning LLMs on clinical reasoning tasks 
to improve the quality and consistency of generated rules, 
and extending the framework to additional diseases to demonstrate scalability in diverse diagnostic settings.

\newpage
\bibliographystyle{unsrt}
\bibliography{bib}

>>>>

This paper presents \sys, a framework for disease prediction using LLMs and ASP. 
The system uses LLMs to extract knowledge from medical texts and translate it into ASP rules, 
which then drive predictions and provide interpretable explanations. 
The architecture, prompt design, and rule structuring in the knowledge base are described.
Experiments show that \sys can predict diseases accurately 
while keeping the reasoning process transparent.

Future work will focus on grounding ASP rules in reliable sources 
through retrieval-augmented generation, fine-tuning LLMs for clinical reasoning, 
and scaling the framework to cover a wider range of diseases.
\newpage
\bibliographystyle{unsrt}
\bibliography{bib}
